Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-28 publication/manuscript.Rmd
remove acknowledgements; add declarations

Acknowledgements {-}
==========
This work has been funded by the German Federal Ministry of Education and Research (BMBF) under Grant No. 01IS18036A and by the Bavarian Ministry of Economic Affairs, Regional Development and Energy through the Center for Analytics – Data – Applications (ADA-Center) within the framework of „BAYERN DIGITAL II“ (20-3410-2-9-8).
The authors of this work take full responsibilities for its content.

Declarations of interest {-}
==========
none

>>>>

## Declarations

### Funding
This work has been funded by the German Federal Ministry of Education and Research (BMBF) under Grant No. 01IS18036A and by the Bavarian Ministry of Economic Affairs, Regional Development and Energy through the Center for Analytics – Data – Applications (ADA-Center) within the framework of „BAYERN DIGITAL II“ (20-3410-2-9-8).

### Conflicts of Interest
None.

### Availability of Data and Material
\url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}

### Code Availability
\url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}
